Understanding the Lomb-Scargle Periodogram\\ {\it (Draft Version \today)}

### 2017-03-28 PracticalLombScargle.tex
More figure and text tweaks

\begin{abstract}
The Lomb-Scargle periodogram is a well-known algorithm for detecting and
characterizing periodic signals in unevenly-sampled data.
This paper presents a conceptual introduction to the Lomb-Scargle periodogram
and important practical considerations for its use.
Rather than a rigorous mathematical treatment, the goal of this paper is to
build intuition about what assumptions are implicit in the use of the
periodogram, so as to motivate important practical considerations required
in its application and interpretation.
\end{abstract}

@@

The Lomb-Scargle periodogram \citep{Lomb76, Scargle82}
is a well-known algorithm for detecting periodicity in unevenly-sampled
time-series, and has seen particularly wide use within the astronomy community.
As an example of a typical application of this method,
consider the data shown in \fig{LINEAR-data}:
this is an irregularly-sampled timeseries showing a single object from the
LINEAR survey \citep{LINEAR1, LINEAR3}, with un-filtered magnitude measured
280 times over the course of five and a half years.
By eye, it is clear that the brightness of the object varies in time with a
range spanning approximately 0.8 magnitudes, but what is not immediately clear
is that this variation is periodic in time.
The Lomb-Scargle periodogram is a method that allows efficient computation of
a Fourier-like power spectrum from such unevenly-sampled data, resulting in
an intuitive means of determining the period of oscillation.

@@

The left panel of \fig{LINEAR-power} and its inset show the Lomb-Scargle
periodogram computed for the data in \fig{LINEAR-data}.
Computing the Lomb-Scargle periodogram for the data gives us a measure of the
power as a function of period of oscillation (\fig{LINEAR-power}, left), from
which we can determine the period of oscillation of approximately 2.58 hours.
The right panel of \fig{LINEAR-power} shows a folded visualization of
the same data as \fig{LINEAR-data} -- i.e.{} plotted as a function of phase
rather than time.

Often this is exactly how the Lomb-Scargle periodogram is presented: as a
clean, well-defined procedure to generate a power spectrum and to
detect the periodic component in an unevenly-sampled dataset.
In practice, however, there are a number of subtle issues that must be
considered when applying a Lomb-Scargle analysis to real-world datasets.
Here are a few questions in particular that we might wish to ask about
the results in \fig{LINEAR-power}:
\begin{enumerate}
  \item How does the Lomb-Scargle periodogram relate to the classical
    Fourier power spectrum?
  \item What is the source of the pattern of multiple peaks revealed by the
    Lomb-Scargle Periodogram?
  \item What is the largest frequency (i.e. Nyquist-like limit) that such
    an analysis is sensitive to?
  \item How should we choose the spacing of the frequency grid for our
    periodogram?
  \item What assumptions does the Lomb-Scargle approach make regarding the
    form of the unknown signal?
  \item How should we understand and report the uncertainty of the
    determined frequency?
\end{enumerate}
Quantitative treatments of these sorts of questions are presented in various
textbooks and review papers, but I have not come across any single concise
reference that gives a good intuition for how to think about such questions.
This paper seeks to fill that gap, and provide a practical,
just-technical-enough guide to the effective use of the Lomb-Scargle method
for detection and characterization of periodic signals.
This paper does not seek a complete or rigorous treatment of the mathematics
involved, but rather seeks to develop the intuition of {\it how} to think
about these questions.

@@

Even limiting our focus to point observations, there are a large number of
complementary techniques for periodic analysis, which generally can be
categorized into a few broad categories:
\begin{description}
  \item[Fourier Methods] are based on the Fourier transform, power spectra,
    and closely related correlation functions. These methods include the
    Schuster periodogram \citep{Schuster98}, the Lomb-Scargle periodogram
    \citep{Lomb76, Scargle82}, the correlation-based method of
    \citet{Edelson88}, and related approaches
    \citep[see also][for a discussion of wavelet transforms in this
      context]{Foster96}.
  \item[Phase-folding Methods] depend on folding
    observations as a function of phase, computing a cost function across
    the phased data (often within bins constructed across phase space)
    and optimizing this cost function across candidate frequencies.
    Some examples are
    String Length \citep{Dworetsky83},
    Analysis of Variance \citep{Schwarzenberg-Czerny89},
    Phase Dispersion Minimization \citep{Stellingwerf78},
    the Gregory-Laredo method \citep{Gregory92},
    and the conditional entropy method \citep{Graham2013}.
    Methods based on correntropy are similar in spirit, but do not always
    require explicit phase folding \citep{Huijse2011,Huijse2012}.
  \item[Least Squares Methods] involve fitting a model to the data at each
    candidate frequency, and selecting the frequency which maximizes the likelihood.
    The Lomb-Scargle periodogram also falls in this category
    (see \sect{schuster-to-lomb-scargle}), as does the Supersmoother approach
    \citep{Reimann94}. Other studies recommend statistics other than
    least square residuals; see, e.g., the orthogonal polynomial fits of
    \citet{Schwarzenberg-Czerny96}.
  \item[Bayesian Approaches] apply Bayesian probability theory to the problem,
    often in a similar manner to the phase-folding and/or least-squares
    approaches.
    Examples are the generalized Lomb-Scargle models of \citet{Bretthorst88},
    the phase-binning model of \citet{Gregory92}, Gaussian process models
    \citep[e.g.][]{Wang2012}, and models based on stochastic processes
    \citep[e.g.][]{Kelly14}.
\end{description}
Various reviews have been undertaken to compare the efficiency and effectiveness
of the available methods; for example, \citet{Schwarzenberg-Czerny99}
focuses on the statistical properties of methods and recommends those
based on smooth model fits over methods based on phase binning,
while \citet{Graham2013b} instead take an empirical approach and find that
when considering detection efficiency in real datasets, no suitably efficient
algorithm universally outperforms the others.

@@

Further, if we compute the squared amplitude of the resulting transform, we
can both do away with complex components and remove the phase imparted by
the choice of temporal baseline; this squared amplitude is usually known as the
{\it power spectral density} or the {\it power spectrum}:
\begin{equation}
  \mathcal{P}_g \equiv \left|\mathcal{F}\{g\}\right|^2
  \eqlabel{power-spectrum}
\end{equation}
The power spectrum of a function is a positive real-valued function of the
frequency $f$ that quantifies the contribution of each frequency $f$ to
the total signal.
Note that if $g$ is real-valued, it follows that $P_g$ is an even function;
{i.e.} $\mathcal{P}_g(f) = \mathcal{P}_g(-f)$.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig08_comb_window_2}
  \caption{Repeating the visualization from \fig{comb-window-1}, but here with
    a lower sampling rate. The result is that the Fourier transform of the
    window function (lower left) has spacing narrower than the Fourier transform
    of the signal (middle left), meaning the observed Fourier transform has
    aliasing of signals, such that not all frequency information can be
    recovered. This is the reason for the famous Nyquist sampling theorem,
    which conceptually says that only a function whose Fourier transform can
    fit entirely between the ``teeth'' of the comb is able to be fully
    recovered for regularly-spaced observations.
    \figlabel{comb-window-2}}
\end{figure}

@@

With the discrete Fourier transform defined in \eqs{DFT-f}{DFT}, we can
apply the definition of the Fourier power spectrum from \eq{power-spectrum}
to compute the {\it Classical Periodogram}, sometimes called the
{\it Schuster Periodogram} after \citet{Schuster98} who first proposed it:
\begin{equation}
  P_S(f) = \frac{1}{N}\left|\sum_{n=1}^N g_n e^{-2\pi i f t_n}\right|^2
  \eqlabel{schuster-periodogram}
\end{equation}
Apart from the $1/N$ proportionality, this sum is precisely the Fourier power
spectrum in \eq{power-spectrum}, computed for a continuous signal observed
with uniform sampling defined by a Dirac comb.
It follows that, in the uniform sampling case, the Schuster periodogram
captures all of the relevant frequency information present in the data.
This definition readily generalizes to the non-uniform case, which we
will explore in the following section.

@@

Finally, there has been some exploration of extensions to the Lomb-Scargle
periodogram for use with multi-band observations, using various forms of
regularization to control model complexity \citep{VanderPlas2015, Long2016}.
With many of these least-squares and/or Bayesian extensions,
computational complexity quickly becomes an issue, because fast
$\mathcal{O}(N\log N)$ approaches which can be used for sinusoidal fits
(see \sect{algorithmic-considerations}) are not available for more general
functional forms, though there is some promising work in this area: see,
for example, the {\it Fast Template Periodogram} (Hoffman et al. 2017,
{\it in prep}\footnote{\url{http://ascl.net/code/v/1559}})
which can quickly construct periodograms from Fourier approximations to templates.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig26_peak_width_height}
  \caption{The effect of the number of points $N$ and the signal-to-noise
    ratio $S/N$ on the expected width and height of the periodogram peak.
    Top panels show the normalized periodogram (\eq{lomb-scargle-normalized}),
    while bottom panels show the PSD-normalized periodogram
    (\eq{lomb-scargle-periodogram})
    Perhaps surprisingly, neither the number of points nor the signal-to-noise
    ratio affects the peak width. \figlabel{peak-width-height}}
\end{figure}

@@

As discussed in \sect{schuster-to-lomb-scargle}, the Lomb-Scargle approach has
two distinct benefits over the classical periodogram:
the noise distribution at each individual frequency is chi-square distributed
under the null hypothesis,
and the result is equivalent to a periodogram derived
from a least squares analysis.
But somehow along the way, a mythology seems to have developed surrounding
the efficiency and efficacy of the Lomb-Scargle approach. In particular,
it's common to see statements or implications along the lines of the following:
\begin{itemize}
  \item {\it Myth: The Lomb-Scargle periodogram can be computed more efficiently
    than the classical periodogram.} Reality: computationally, the two
    are quite similar, and in fact the fastest Lomb-Scargle algorithm currently
    available is based on the classical periodogram computed via the
    the NFFT algorithm (see \sect{algorithmic-considerations}).
  \item {\it Myth: The Lomb-Scargle periodogram is faster than a direct
    least squares periodogram because it avoids explicitly solving for
    model coefficients.}
    Reality: model coefficients can be determined with little extra
    computation \citep[see the discussion in][]{ICVG2014}.
  \item {\it Myth: The Lomb-Scargle periodogram allows analytic computation of
    statistics for periodogram peaks.} Reality: while this is true at
    individual frequencies, it is not true for the more relevant question of
    maximum peak heights across multiple frequencies,
    which must be either approximated
    or computed by bootstrap resampling (see \sect{uncertainties})
  \item {\it Myth: The Lomb-Scargle periodogram corrects for aliasing due to
    sampling and leads to independent noise at each frequency.}
    Reality: for structured window functions common to most astronomical
    applications, the Lomb-Scargle
    periodogram has the same window-driven issues as the classical
    periodogram, including spurious peaks due to partial aliasing, and
    highly correlated periodogram errors (see \sect{failure-modes}).
  \item {\it Myth: Bayesian analysis shows that Lomb-Scargle is the optimal
    statistic for detecting periodic signals in data.} Reality: Bayesian
    analysis shows that Lomb-Scargle is the optimal statistic for
    {\it fitting a sinusoid to data}, which is not the same as saying it
    is optimal for finding the frequency of a generic, potentially
    non-sinusoidal signal (see \sect{bayesian-periodograms}).
\end{itemize}
With these myths set aside, what is the practical advantage of Lomb-Scargle
over a classical periodogram?
What would we lose if we instead used a simple Fourier periodogram,
estimating uncertainty, significance, and false alarm probability by
resampling and simulation, as we must for Lomb-Scargle itself?

@@

Conversely, if you replace your Lomb-Scargle approach with a classical periodogram,
what you gain is the ability to reason quantitatively about the effects of the
survey window function on the resulting periodogram (see \sect{CLEAN}).
While the deconvolution problem is ill-posed, there is no reason to assume
this is a fatal defect: ill-posed linear models are solved routinely in
other areas of computational research, particularly by using priors or
various forms of regularization.
In any case, I would contend that there is ample room for practitioners to
question the prevailing folk wisdom of the advantage of Lomb-Scargle
over approaches based directly on the Fourier transform and classical
periodogram.

@@

\acknowledgments
{\it Acknowledgments:} I am grateful to Jeff Scargle, Max Mahlke, Dan
Foreman-Mackey, and Zeljko Ivezic for helpful feedback
on early drafts of this paper.
This work was supported by the University of Washington eScience Institute,
with funding from the Gordon and Betty Moore Foundation, the Alfred P. Sloan
Foundation, and the Washington Research Foundation.

>>>>

\begin{abstract}
The Lomb-Scargle periodogram is a well-known algorithm for detecting and
characterizing periodic signals in unevenly-sampled data.
This paper presents a conceptual introduction to the Lomb-Scargle periodogram
and important practical considerations for its use.
Rather than a rigorous mathematical treatment, the goal of this paper is to
build intuition about what assumptions are implicit in the use of the
Lomb-Scargle periodogram and related estimators of periodicity,
so as to motivate important practical considerations required
in its proper application and interpretation.
\end{abstract}

@@

The Lomb-Scargle periodogram \citep{Lomb76, Scargle82}
is a well-known algorithm for detecting and characterizing
periodicity in unevenly-sampled
time-series, and has seen particularly wide use within the astronomy community.
As an example of a typical application of this method,
consider the data shown in \fig{LINEAR-data}:
this is an irregularly-sampled timeseries showing a single object from the
LINEAR survey \citep{LINEAR1, LINEAR3}, with un-filtered magnitude measured
280 times over the course of five and a half years.
By eye, it is clear that the brightness of the object varies in time with a
range spanning approximately 0.8 magnitudes, but what is not immediately clear
is that this variation is periodic in time.
The Lomb-Scargle periodogram is a method that allows efficient computation of
a Fourier-like power spectrum estimator from such unevenly-sampled data,
resulting in an intuitive means of determining the period of oscillation.

@@

The Lomb-Scargle periodogram computed from this data is shown in the left
panel  of \fig{LINEAR-data}.
The Lomb-Scargle periodogram here yields an estimate of the Fourier
power as a function of period of oscillation (\fig{LINEAR-power}, left), from
which we can read-off the period of oscillation of approximately 2.58 hours.
The right panel of \fig{LINEAR-power} shows a folded visualization of
the same data as \fig{LINEAR-data} -- i.e.{} plotted as a function of phase
rather than time.

Often this is exactly how the Lomb-Scargle periodogram is presented: as a
clean, well-defined procedure to generate a power spectrum and to
detect the periodic component in an unevenly-sampled dataset.
In practice, however, there are a number of subtle issues that must be
considered when applying a Lomb-Scargle analysis to real-world datasets.
Here are a few questions in particular that we might wish to ask about
the results in \fig{LINEAR-power}:
\begin{enumerate}
  \item How does the Lomb-Scargle periodogram relate to the classical
    Fourier power spectrum?
  \item What is the source of the pattern of multiple peaks revealed by the
    Lomb-Scargle Periodogram?
  \item What is the largest frequency (i.e. Nyquist-like limit) that such
    an analysis is sensitive to?
  \item How should we choose the spacing of the frequency grid for our
    periodogram?
  \item What assumptions, if any, does the Lomb-Scargle approach make
    regarding the form of the unknown signal?
  \item How should we understand and report the uncertainty of the
    determined frequency?
\end{enumerate}
Quantitative treatments of these sorts of questions are presented in various
textbooks and review papers, but I have not come across any single concise
reference that gives a good intuition for how to think about such questions.
This paper seeks to fill that gap, and provide a practical,
just-technical-enough guide to the effective use of the Lomb-Scargle method
for detection and characterization of periodic signals.
This paper does not seek a complete or rigorous treatment of the mathematics
involved, but rather seeks to develop the intuition of {\it how} to think
about these questions, with references to relevant technical treatments.

@@

Even limiting our focus to point observations, there are a large number of
complementary techniques for periodic analysis, which generally can be
categorized into a few broad categories:
\begin{description}
  \item[Fourier Methods] are based on the Fourier transform, power spectra,
    and closely related correlation functions. These methods include the
    classical or Schuster periodogram \citep{Schuster98},
    the Lomb-Scargle periodogram
    \citep{Lomb76, Scargle82}, the correlation-based method of
    \citet{Edelson88}, and related approaches
    \citep[see also][for a discussion of wavelet transforms in this
      context]{Foster96}.
  \item[Phase-folding Methods] depend on folding
    observations as a function of phase, computing a cost function across
    the phased data (often within bins constructed across phase space)
    and optimizing this cost function across candidate frequencies.
    Some examples are
    String Length \citep{Dworetsky83},
    Analysis of Variance \citep{Schwarzenberg-Czerny89},
    Phase Dispersion Minimization \citep{Stellingwerf78},
    the Gregory-Laredo method \citep{Gregory92},
    and the conditional entropy method \citep{Graham2013}.
    Methods based on correntropy are similar in spirit, but do not always
    require explicit phase folding \citep{Huijse2011,Huijse2012}.
  \item[Least Squares Methods] involve fitting a model to the data at each
    candidate frequency, and selecting the frequency which maximizes the likelihood.
    The Lomb-Scargle periodogram also falls in this category
    (see \sect{schuster-to-lomb-scargle}), as does the Supersmoother approach
    \citep{Reimann94}. Other studies recommend statistics other than
    least square residuals; see, e.g., the orthogonal polynomial fits of
    \citet{Schwarzenberg-Czerny96}.
  \item[Bayesian Approaches] apply Bayesian probability theory to the problem,
    often in a similar manner to the phase-folding and/or least-squares
    approaches.
    Examples are the generalized Lomb-Scargle models of \citet{Bretthorst88},
    the phase-binning model of \citet{Gregory92}, Gaussian process models
    \citep[e.g.][]{Wang2012}, and models based on stochastic processes
    \citep[e.g.][]{Kelly14}.
\end{description}
Various reviews have been undertaken to compare the efficiency and effectiveness
of the available methods; for example, \citet{Schwarzenberg-Czerny99}
focuses on the statistical properties of methods and recommends those
based on smooth model fits over methods based on phase binning,
while \citet{Graham2013b} instead take an empirical approach and find that
when considering detection efficiency in real datasets, no suitably efficient
algorithm universally outperforms the others.

@@

Further, if we compute the squared amplitude of the resulting transform, we
can both do away with complex components and remove the phase imparted by
the choice of temporal baseline; this squared amplitude is usually known as the
{\it power spectral density} or simply the {\it power spectrum}:
\begin{equation}
  \mathcal{P}_g \equiv \left|\mathcal{F}\{g\}\right|^2
  \eqlabel{power-spectrum}
\end{equation}
The power spectrum of a function is a positive real-valued function of the
frequency $f$ that quantifies the contribution of each frequency $f$ to
the total signal.
Note that if $g$ is real-valued, it follows that $P_g$ is an even function;
{i.e.} $\mathcal{P}_g(f) = \mathcal{P}_g(-f)$.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig08_comb_window_2}
  \caption{Repeating the visualization from \fig{comb-window-1}, but here with
    a lower sampling rate. The result is that the Fourier transform of the
    window function (middle right) has spacing narrower than the Fourier
    transform of the signal (upper right), meaning the observed Fourier
    transform (lower right) has
    aliasing of signals, such that not all frequency information can be
    recovered. This is the reason for the famous Nyquist sampling theorem,
    which conceptually says that only a function whose Fourier transform can
    fit entirely between the ``teeth'' of the comb is able to be fully
    recovered for regularly-spaced observations.
    \figlabel{comb-window-2}}
\end{figure}

@@

With the discrete Fourier transform defined in \eqs{DFT-f}{DFT}, we can
apply the definition of the Fourier power spectrum from \eq{power-spectrum}
to compute the {\it classical periodogram}, sometimes called the
{\it Schuster periodogram} after \citet{Schuster98} who first proposed it:
\begin{equation}
  P_S(f) = \frac{1}{N}\left|\sum_{n=1}^N g_n e^{-2\pi i f t_n}\right|^2
  \eqlabel{schuster-periodogram}
\end{equation}
Apart from the $1/N$ proportionality, this sum is precisely the Fourier power
spectrum in \eq{power-spectrum}, computed for a continuous signal observed
with uniform sampling defined by a Dirac comb.
It follows that, in the uniform sampling case, the Schuster periodogram
captures all of the relevant frequency information present in the data.
This definition readily generalizes to the non-uniform case, which we
will explore in the following section.

@@

Finally, there has been some exploration of extensions to the Lomb-Scargle
periodogram for use with multi-band observations, using various forms of
regularization to control model complexity \citep{VanderPlas2015, Long2016}.
With many of these least-squares and/or Bayesian extensions,
computational complexity quickly becomes an issue, because fast
$\mathcal{O}(N\log N)$ approaches which can be used for sinusoidal fits
(see \sect{algorithmic-considerations}) are not available for more general
functional forms, though there is some promising work in this area: see,
for example, the {\it Fast Template Periodogram}\footnote{\url{http://ascl.net/code/v/1559}}
(Hoffman et al. 2017, {\it in prep})
which can quickly construct periodograms from Fourier approximations to templates.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig26_peak_width_height}
  \caption{The effect of the number of points $N$ and the signal-to-noise
    ratio $S/N$ on the expected width and height of the periodogram peak.
    Top panels show the normalized periodogram (\eq{lomb-scargle-normalized}),
    while bottom panels show the PSD-normalized periodogram
    (\eq{lomb-scargle-periodogram}) scaled by noise variance.
    Perhaps surprisingly, neither the number of points nor the signal-to-noise
    ratio affects the peak width. \figlabel{peak-width-height}}
\end{figure}

@@

As discussed in \sect{schuster-to-lomb-scargle}, the Lomb-Scargle approach has
two distinct benefits over the classical periodogram:
the noise distribution at each individual frequency is chi-square distributed
under the null hypothesis,
and the result is equivalent to a periodogram derived
from a least squares analysis.
But somehow along the way, a mythology seems to have developed surrounding
the efficiency and efficacy of the Lomb-Scargle approach. In particular,
it's common to see statements or implications along the lines of the following:
\begin{itemize}
  \item {\it Myth: The Lomb-Scargle periodogram can be computed more efficiently
    than the classical periodogram.} Reality: computationally, the two
    are quite similar, and in fact the fastest Lomb-Scargle algorithm currently
    available is based on the classical periodogram computed via the
    the NFFT algorithm (see \sect{algorithmic-considerations}).
  \item {\it Myth: The Lomb-Scargle periodogram is faster than a direct
    least squares periodogram because it avoids explicitly solving for
    model coefficients.}
    Reality: model coefficients can be determined with little extra
    computation \citep[see the discussion in][]{ICVG2014}.
  \item {\it Myth: The Lomb-Scargle periodogram allows analytic computation of
    statistics for periodogram peaks.} Reality: while this is true at
    individual frequencies, it is not true for the more relevant question of
    maximum peak heights across multiple frequencies,
    which must be either approximated
    or computed by bootstrap resampling (see \sect{uncertainties})
  \item {\it Myth: The Lomb-Scargle periodogram corrects for aliasing due to
    sampling and leads to independent noise at each frequency.}
    Reality: for structured window functions common to most astronomical
    applications, the Lomb-Scargle
    periodogram has the same window-driven issues as the classical
    periodogram, including spurious peaks due to partial aliasing, and
    highly correlated periodogram errors (see \sect{failure-modes}).
  \item {\it Myth: Bayesian analysis shows that Lomb-Scargle is the optimal
    statistic for detecting periodic signals in data.} Reality: Bayesian
    analysis shows that Lomb-Scargle is the optimal statistic for
    {\it fitting a sinusoid to data}, which is not the same as saying it
    is optimal for finding the frequency of a generic, potentially
    non-sinusoidal signal (see \sect{bayesian-periodograms}).
\end{itemize}
With these misconceptions corrected, what is the practical advantage of
Lomb-Scargle over a classical periodogram?
What would we lose if we instead used the simple classical Fourier periodogram,
estimating uncertainty, significance, and false alarm probability by
resampling and simulation, as we must for Lomb-Scargle itself?

@@

Conversely, if you replace your Lomb-Scargle approach with a classical periodogram,
what you gain is the ability to reason quantitatively about the effects of the
survey window function on the resulting periodogram (cf. \sect{CLEAN}).
While the deconvolution problem is ill-posed, there is no reason to assume
this is a fatal defect: ill-posed linear models are solved routinely in
other areas of computational research, particularly by using sparsity
priors or various forms of regularization.
In any case, I would contend that there is ample room for practitioners to
question the prevailing folk wisdom of the advantage of Lomb-Scargle
over approaches based directly on the Fourier transform and classical
periodogram.

@@

\acknowledgments
{\it Acknowledgments:} I am grateful to Jeff Scargle, Max Mahlke, Dan
Foreman-Mackey, Zeljko Ivezic, and David Hogg for helpful feedback
on early drafts of this paper.
This work was supported by the University of Washington eScience Institute,
with funding from the Gordon and Betty Moore Foundation, the Alfred P. Sloan
Foundation, and the Washington Research Foundation.
